Appendix A : Dipole-dipole interaction between two spins in solid

### 2022-07-12 Manuscrit Thèse/chapter 2/Appendix dipole-dipole.tex
la tete de tes morts

\documentclass[a4paper]{book}
\usepackage[]{amsmath}
\usepackage[]{physics} % \bra, \ket etc
\usepackage{graphicx} %Pour les figures je crois
\usepackage{hyperref}
\usepackage[
    %backend=biber, 
    natbib=true,
    style=numeric,
    sorting=none, %Pour faire apparaitre les refs dans l'ordre
    hyperref=true
]{biblatex} %Imports biblatex package
\addbibresource{Bib_ch2.bib} %Import the bibliography file

@@

\title{Appendix A : Dipole-dipole interaction between two spins in solid}
\begin{document}
\section{The dipole-dipole Hamiltonian}
The dipole-dipole interaction between two point-like magnetic dipoles can be derived classically by computing the static magnetic field generated by one dipole at the position of the second dipole.

@@

\section{Flip-Flops, double flips and cross-relaxations}

@@

%réécris moi ça, c'est naze
When two spin populations of different polarization can be resonantly coupled by either flip-flop or double-flip, cross-relaxation happens, that is a macroscopic transfer of polarization from the most polarized spin group to the least polarized one.

>>>>

\documentclass[a4paper]{report}
\usepackage[]{amsmath}
\usepackage[]{physics} % \bra, \ket etc
\usepackage{graphicx} %Pour les figures je crois
\usepackage{hyperref}
\usepackage[
    %backend=biber, 
    natbib=true,
    style=numeric,
    sorting=none, %Pour faire apparaitre les refs dans l'ordre
    hyperref=true
]{biblatex} %Imports biblatex package
\addbibresource{Bib_ch2.bib} %Import the bibliography file

@@

\title{Appendix A : Dipole-dipole interaction between two spins in solid}
\begin{document}
\chapter{Detection of dark spins via cross-relaxations}
In this chapter, we will see how...
\section{The dipole-dipole Hamiltonian}
The dipole-dipole interaction between two point-like magnetic dipoles can be derived classically by computing the static magnetic field generated by one dipole at the position of the second dipole.

@@

\section{Flip-Flops, double flips and cross-relaxation}

\begin{figure}
\includegraphics[width=0.9\textwidth]{Figures/Shema_CR}
\caption{Illustration of cross-relaxations between an NV center and an unpolarized spin. Red dots represent the population in each states, and the arrows the various population transfer mechanisms}
\label{CR_shema}
\end{figure}

@@

Cross-relaxation (CR) is the transfer of polarization from one spin to another (or more generally from one family of spins to another family). This process con occur either through flip-flops, or through double flips, as long as the resonance condition between the two spins is met.

Fig. \ref{CR_shema} illustrates CR between a polarized NV center and an unpolarized second spin. When the two considered spin transitions become resonant, in this case by tuning a magnetic field, polarization from the NV center will be transferred to the second spin, meaning in this case that the NV center will end up less polarized and the second spin more polarized.

\section{Detection of dark spins with NV centers via cross-relaxations}
